Multi-line Intensity Mapping

### 2019-04-27 paper/ms.tex
Add basic stuff about interloping lines

@@

For the variance and covariance of the power spectra, it can be shown that,
\beq\label{eq:var_cov}
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
\xps{i}{j}\xps{i}{k}\text{,}
\end{split}
\eeq
where $\pstot{i} \equiv \ps{i} + N_i$. Note that $N_i$ contains contributions
from instrument noise, residual foreground contamination, and
interloping/extraloping lines. While computing the Fisher matrix numerically
is trivial, we will first work out the noise-dominated case which has a
somewhat tractable analytic solution.

@@

\subsection{Three-field \CO{} Forecasts for CCAT-p} \label{ssec:forecasts_tf}
% \begin{figure}[h!]
% \begin{center}
% \includegraphics{fig/CO_tf.pdf}
% \end{center}
% \caption{Constraints that can be placed on the fluctuations of the \CO(6-5),
% \CO(5-4), and \CO(4-3) lines with CCAT-p at $z_{\text{obs}} = 0.88$. This
% Figure is purely illustrative, as we do not include noise contributions from
% residual foreground contamination or interloper/extraloper lines. According to
% our simple \CO{} model, we have that $B_{\text{6-5}}, B_{\text{5-4}},
% B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$. Using the instrumental
% specifications in \citet{2018arXiv181208135C}, we find that $N_{\text{6-5}},
% N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9, 1.4\times10^9,
% 5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We find the same
% behavior as in Figure~\ref{fig:tf_Nconst}, where the best-measured line is
% strongly negatively degenerate with the second-best measured line, the
% best-measured and worst-measured are slightly negatively degenerate, and the
% second-best measured line and the worst-measured are slightly positively
% degenerate. }
% \label{fig:CO_tf}
% \end{figure}

>>>>

\newcommand{\kpar}{k_{\parallel}}
\newcommand{\kperp}{\bm{k}_{\perp}}
\newcommand{\apar}{\alpha_{\parallel}}
\newcommand{\aperp}{\alpha_{\perp}}

@@

For the variance and covariance of the power spectra, it can be shown that,
\beq\label{eq:var_cov}
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
\xps{i}{j}\xps{i}{k}\text{,}
\end{split}
\eeq
where $\pstot{i} = \ps{i} + N_i$. Note that $N_i$ contains contributions
from instrument noise, residual foreground contamination, and
interloping/extraloping lines. While computing the Fisher matrix numerically
is trivial, we will first work out the noise-dominated case which has a
somewhat tractable analytic solution.

@@

\subsection{Interloping Lines} \label{ssec:interlopers}
The multi-field method relies only on the measurements of cross-spectra beween
various lines. Interloping lines do not contribute to the average
cross-spectra signal, but does contribute to the noise of the measurement. We
can account for this by modifying the equation for $N_i$ to be
\citep{2016ApJ...825..143L, 2016ApJ...832..165C},
\beq\label{eq:ptot_intlpr}
N_i = N_{i,\text{instrumental}} + \sum_{j} \frac{1}{\apar(z_j) \aperp(z_j)^2} 
            P_j\left(\frac{\kpar}{\apar(z_j)}, 
                     \frac{\kperp}{\aperp(z_j)}\right)\text{,}
\eeq
where $N_{i,\text{instrumental}}$ is the instrumental noise of line $i$ at the
observed frequency, the sum on $j$ is over all interloping lines, $z_j$ is the
emitted redshift of line $j$, and where,
\begin{alignat}{2}
\apar = \frac{H(z_i)}{H(z_j)} \frac{1+z_j}{1+z_i} \quad \quad &&
\aperp = \frac{D_{A}(z_j)}{D_A(z_i)}\text{,}
\end{alignat}
where $z_i$ is the emitted redshift of line $i$ and $D_A(z)$ is the comoving
angular diameter distance to redshift $z$.

For simplicity, we assume the instrumental noise is white (i.e.
$N_{i,\text{instrumental}}$ is constant).

% \begin{multicols}{2}
%   \beq
%     \apar = \frac{H(z_i)}{H(z_j)} \frac{1+z_j}{1+z_i}
%   \eeq\break
%   \beq
%     \aperp = \frac{D_{A}(z_j)}{D_A(z_i)}
%   \eeq
% \end{multicols}

% \begin{figure}[h!]
% \begin{center}
% \includegraphics{fig/CO_tf.pdf}
% \end{center}
% \caption{Constraints that can be placed on the fluctuations of the \CO(6-5),
% \CO(5-4), and \CO(4-3) lines with CCAT-p at $z_{\text{obs}} = 0.88$. This
% Figure is purely illustrative, as we do not include noise contributions from
% residual foreground contamination or interloper/extraloper lines. According to
% our simple \CO{} model, we have that $B_{\text{6-5}}, B_{\text{5-4}},
% B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$. Using the instrumental
% specifications in \citet{2018arXiv181208135C}, we find that $N_{\text{6-5}},
% N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9, 1.4\times10^9,
% 5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We find the same
% behavior as in Figure~\ref{fig:tf_Nconst}, where the best-measured line is
% strongly negatively degenerate with the second-best measured line, the
% best-measured and worst-measured are slightly negatively degenerate, and the
% second-best measured line and the worst-measured are slightly positively
% degenerate. }
% \label{fig:CO_tf}
% \end{figure}
